### 2024-11-20 cv2/cv.tex
CV updates

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
%\renewcommand{\familydefault}{\sfdefault}

@@

\headleft{Profile}
 Hands-on technical team leader, {\bf applied math} researcher and engineer at heart, with a specialist expertise in {\bf computer vision} and {\bf computer graphics}.

@@

{\sc Head of AI.} {\it Didimo}, Porto, Portugal.  \dates{Sep 2019--present} \\
\smaller{Leading development of automated 3D character creation for {\em Popul8} software: shape reconstruction / generation, rig retargeting, skin texturing, asset fitting, \ldots}

@@

\is 
{\sc Scientific reporting:} Author of 106 peer-reviewed scientific articles and 6 published international patents.

>>>>

%\usepackage{FiraSans}        % Change this to use any font, but keep it simple
%\renewcommand{\familydefault}{\sfdefault}

@@

\headleft{Profile}
 Hands-on technical team leader, {\bf applied math} research engineer at heart, with a specialist expertise in {\bf computer vision} and {\bf computer graphics}.

@@

{\sc Head of Artificial Intelligence.} {\it Didimo}, Porto, Portugal. \hphantom{CACACACA} \dates{Sep 2019--present} \\
\smaller{Leading development of automated 3D character creation for {\em Popul8} software: shape reconstruction / generation, rig retargeting, skin texturing, asset fitting, mesh wrapping.}

@@

\is 
{\sc Scientific writing:} Author of 106 peer-reviewed scientific articles and 6 published international patents. 7847 citations, {\em h}-index: 35.
